---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem2

## 2(a)
```{r}
# import the data
address = getwd()
files = paste(address, "6data.csv", sep = "/")
data = read.csv(file = files)

# use the multiple linear regression model to fit

fit <- lm(Y~., data = data)
summary(fit)
```
Conduct a hypothesis test for the overall utility of the model

Hypothesis: $H_0:$ $\beta_1=\beta_2=\beta_3=\beta_4=0$ v.s. $H_1:$ at least one $\beta_j\neq0$ for $j=1,2,3,4$

Then under $H_0$, we have 
$$
F(\boldsymbol{H})\sim F_{\{q,N-k-1 \}}=F_{\{4,35 \}}
$$

Then according to the ANOVA table, we have F statistic: 26.84 on 4 and 35 DF,  p-value: 3.088e-10, which is very significant.

We can not reject the $H_0:$ $\beta_1=\beta_2=\beta_3=\beta_4=0$
And we can conclude that the model is useful for the prediction of rental rates.

## 2(b)

```{r}
# Studentized residuals
r1<-rstandard(fit)

# Studentized deleted residuals
r2<-rstudent(fit)

# Leverage values
h<-hatvalues(fit)

# Dffits
dff<-dffits(fit)

# Cook’s distance
co<-cooks.distance(fit)

# tabulate the results
table<-data.frame(Studentized=r1,Stud_deleted=r2,Leverage_val=h,Dffits=dff,Cooks_dist=co)
table
```

## 2(c)
Identification criterion:

Using the Studentized residuals, considered a point to be an outlier if absolute value of studentized residual is greater than 2.
```{r}
abr1<-abs(r1)
sort(abr1, decreasing = TRUE)[1:5]
```

By the table, we have that the 6th, 8th and 9th observations are high leverage points

## 2(d)
Identification criterion:

The $i$th is an outlier in X point if the leverage value satisfy$h_{ii}\geq 2 \frac{k+1}{n}$
```{r}
# note that mean(h)=(k+1)/n
sort(h, decreasing=TRUE)[1:5]/mean(h)
```

By the table, we have that the 3th and 8th observations are high leverage points

## 2(e)
Consider the Dffits:

The $i$th is a influential observation if $|diffits_{i}|\geq 2\sqrt{\frac{k+1}{n}}$

```{r}
# note that mean(h)=(k+1)/n
f<-sqrt(mean(h))
abdff<-abs(dff)
sort(abdff, decreasing = TRUE)[1:6]/f

```

By the table, we have that the 6th, 8th, 9th, 26th and 38th are observations are influential points

Consider the Cook's distance:

The $i$th is a influential if its Cook's distance is larger than $F_{\{0.05,k+1,n-(k+1)\} }=F_{\{0.05,5,35\} }$

```{r}
g<-qf(0.5,5,35)
g
sort(co, decreasing = TRUE)[1:5]-g
```


By the table, we have that the 8th observation are influential point



